\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)

### 2021-06-25 authors_responses/first_tac_rejection/authors_response.tex
In the processes of explaining the instance-timestep relation better in the main text (not done) Fixed typos in author's response

As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearlising filter for the prediction step of the algorithm. However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag) and has been computed when evaluating the proposed filter through simulation. This can be done in various ways specific to the system being modelled and is beyond the scope of this work.

>>>>

As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearising filter for the prediction step of the algorithm. However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag) and has been computed when evaluating the proposed filter through simulation. This can be done in various ways specific to the system being modelled and is beyond the scope of this work.
